---
title: "Deep Learning Demo"
author: "Prajakta Lahankar"
output:
  prettydoc::html_pretty:
    theme: cayman
    toc: true
    df_print: paged
  pdf_document:
    toc: true
    toc_depth: 3
    highlight: haddock
  tufte::tufte_handout: default
  ioslides_presentation: default
  html_vignette: default
  html_document: 
    toc: true
    toc_depth: 3
    toc_float: true
    theme: cerulean
    highlight: haddock
    df_print: paged
  beamer_presentation: default
---


# House Data
```{r, warning=F, message=F}
data = read.csv('https://raw.githubusercontent.com/pseudorational/data/master/houses.csv')
data = data[,c('price','bedrooms','bathrooms','sqft_living','sqft_lot','floors','waterfront','view','condition','grade','age')]
str(data)
```


## Split Data
```{r, warning=F, message=F}
set.seed(1031)
split = sample(x = c('train','validation','test'),size = nrow(data),replace = T,prob = c(0.4,0.4,0.2))
train = data[split=='train',]
validation = data[split=='validation',]
test = data[split=='test',]
```

# Linear Regression Model
```{r, warning=F, message=F}
linearModel = lm(price~.,data=train)
pred = predict(linearModel,newdata=test)
rmse_linear = sqrt(mean((pred - test$price)^2)); rmse_linear
```

# Deep Learning

## Prepare Data
```{r, warning=F, message=F}
install.packages('h2o')
library(h2o)
h2o.init()
train_h2o = as.h2o(train)
validation_h2o = as.h2o(validation)
test_h2o = as.h2o(test)
```

## Basic Neural Network
Hidden Layer: 1
Hidden Units: 5
```{r, warning=F, message=F}
model1 = h2o.deeplearning(x=2:11,
                          y = 1,
                          training_frame = train_h2o,
                          hidden=c(5),
                          seed=1031)
h2o.performance(model1,newdata=test_h2o)
```

## Deep Learning Model with Two Layers
Hidden Layers: 2
Hidden Units: 5 in each layer
```{r, warning=F, message=F}
model2 = h2o.deeplearning(x=2:11,
                          y = 1,
                          training_frame = train_h2o,
                          hidden=c(5,5),
                          seed=1031)
h2o.performance(model2,newdata=test_h2o)
```

## Deep Learning Model with Three Layers
Hidden Layers: 3
Hidden Units: 10 in each layer
```{r, warning=F, message=F}
model3 = h2o.deeplearning(x=2:11,
                          y = 1,
                          training_frame = train_h2o,
                          hidden=c(10,10,10),
                          seed=1031)
h2o.performance(model3,newdata=test_h2o)
```

## Deep Learning Model
Construct your own Deep Learning Model Architecture
Hidden Layers: ??
Hidden Units: ??
```{r, warning=F, message=F}
model4 = h2o.deeplearning(x=2:11,
                          y = 1,
                          training_frame = train_h2o,
                          hidden=c(20,30,20,30),
                          seed=1031)
h2o.performance(model4,newdata=test_h2o)
```


## Tuned Model
Here is a model obtained from tuning hyperparameters.Hyperparameter tuning code is not here as it takes a long time to run. 
```{r, warning=F, message=F}
model5 = h2o.deeplearning(x=2:11,
                          y=1,
                          training_frame=train_h2o,
                          standardize = T,
                          activation = 'Rectifier',
                          hidden = c(50,50),
                          epochs = 10,
                          seed=1031,
                          adaptive_rate = T,
                          rho=0.99,
                          epsilon = 1e-08, 
                          input_dropout_ratio = 0,
                          l1=7.9e-05,
                          l2=4e-05,
                          max_w2 = 3.4e+38,
                          stopping_metric = 'RMSE',
                          stopping_tolerance = 0.01)
h2o.performance(model5,newdata=test_h2o)
```



